Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-10 vesicle_code/docs/adhesion/adhesion.tex
fixed up figure 6

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement0_adS7em1_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement0_adS7em1_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement0_adS7em1_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement0_adS7em1_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement0_adS7em1_image05.png} \\

  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement2em2_adS7em1_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement2em2_adS7em1_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement2em2_adS7em1_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement2em2_adS7em1_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement2em2_adS7em1_image05.png} \\

  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement1em1_adS7em1_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement1em1_adS7em1_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement1em1_adS7em1_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement1em1_adS7em1_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement1em1_adS7em1_image05.png} \\

  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement1em1_adS6em1_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement1em1_adS6em1_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement1em1_adS6em1_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement1em1_adS6em1_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 0.5cm 4cm 0.5cm},clip]
    {figs/extensional_displacement1em1_adS6em1_image05.png}

  \caption{\label{fig:extensionalNonsymmetric}Dynamics of a vesicle pair in a planar extensional flow. ${\cal H} = 0.7$ for the first three rows, and ${\cal H}=0.6$ for the bottom row. From top to bottom, the initial vertical displacement $\triangle y=0$, 0.02, 0.1 and 0.1. The reduced area is ???, the strain rate $\chi = ???$ and the adhesion distance $\delta = ???$. }
  \end{figure}

>>>>

\begin{figure}[htp]
  \includegraphics[height = 0.2\textwidth,trim={1cm 0cm 1cm 0cm},clip]
    {figs/extensional_displacement0_adS7em1_image01.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement0_adS7em1_image02.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement0_adS7em1_image03.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement0_adS7em1_image04.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement0_adS7em1_image05.png} \\

  \includegraphics[height = 0.2\textwidth,trim={1cm 0cm 1cm 0cm},clip]
    {figs/extensional_displacement2em2_adS7em1_image01.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement2em2_adS7em1_image02.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement2em2_adS7em1_image03.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement2em2_adS7em1_image04.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement2em2_adS7em1_image05.png} \\

  \includegraphics[height = 0.2\textwidth,trim={1cm 0cm 1cm 0cm},clip]
    {figs/extensional_displacement1em1_adS7em1_image01.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS7em1_image02.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS7em1_image03.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS7em1_image04.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS7em1_image05.png} \\

  \includegraphics[height = 0.2\textwidth,trim={1cm 0cm 1cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_image01.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_image02.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_image03.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_image04.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_image05.png}
  \caption{\label{fig:extensionalNonsymmetric}Dynamics of a vesicle pair in a planar extensional flow. ${\cal H} = 0.7$ for the first three rows, and ${\cal H}=0.6$ for the bottom row. From top to bottom, the initial vertical displacement $\triangle y=0$, 0.02, 0.1 and 0.1. The reduced area is ???, the strain rate $\chi = ???$ and the adhesion distance $\delta = ???$. }
  \end{figure}
